---
title: "arima.sim() time series data set (ARIMA.SIM)"
author: "Juan Carlos Bellassai"
date: "22/6/2021"
output: pdf_document
---

# Data format

As in UCR Time Series Archive, each of the data sets comes in two parts, a TRAIN partition and a TEST partition.
For exaample, for **ar1** data set we have two files, _ar1_TEST.csv_ and _ar1_TRAIN.csv_
The two files will be in the same format but are of different sizes.

Unlike UCR, ARIMA.SIM in .csv format.

As in UCR Time Series Archive, there is one time series exemplar per row. The first value in the row is the class label (an integer between 1 and the number of classes). The rest of the row are the data sample values. The order of time series exemplar is in random.


# AR(P)

```{r}
# parameters list (classes)
parameters = c(-.9, -.7, -.5, -.3, -.1, .1, .3, .5, .7, .9)

# create a empty matrix for lead time series
classes = length(parameters) #
n = 200  #number of time series per class
l = 1000 #time series legth 
AR1_TRAIN = matrix(0, classes*n, l+1) 
AR1_TEST = matrix(0, classes*n, l+1)

# create time series
c = 1
for (cla in 1:classes) {
  p = parameters[cla]
  
  for (i in 1:n){
    AR1_TRAIN[c,] = c(cla, arima.sim(n=l, list(ar=p), sd=1))
    AR1_TEST[c,] = c(cla, arima.sim(n=l, list(ar=p), sd=1))
    c = c+1
  }
}

AR1_TRAIN = data.frame(AR1_TRAIN)
colnames(AR1_TRAIN)[1] = "clase"
AR1_TEST = data.frame(AR1_TEST)
colnames(AR1_TEST)[1] = "clase"

```

Let's see an axample for each class. 

```{r}
c = 0
for (i in 1:3){
  ci = c+i
  plot(as.numeric(AR1_TRAIN[ci,2:l+1]), type="l", col=i, 
       ylim=c(-7, 7))
  if (i<classes){par(new=TRUE)}
  c = c+100
}
```

We export as .csv files.

```{r}

```


# MA()

```{r}
# parameters list (classes)
parameters = c(-.9, -.7, -.5, -.3, -.1, .1, .3, .5, .7, .9)

# create a empty matrix for lead time series
classes = length(parameters) #
n = 200  #number of time series per class
l = 1000 #time series length 
MA1_TRAIN = matrix(0, classes*n, l+1) 
MA1_TEST = matrix(0, classes*n, l+1)

# create time series
c = 1
for (cla in 1:classes) {
  p = parameters[cla]
  
  for (i in 1:n){
    MA1_TRAIN[c,] = c(cla, arima.sim(n=l, list(ma=p), sd=1))
    MA1_TEST[c,] = c(cla, arima.sim(n=l, list(ma=p), sd=1))
    c = c+1
  }
}

MA1_TRAIN = data.frame(MA1_TRAIN)
colnames(MA1_TRAIN)[1] = "clase"
MA1_TEST = data.frame(MA1_TEST)
colnames(MA1_TEST)[1] = "clase"
```

```{r}
c = 0
for (i in 1:3){
  ci = c+i
  plot(as.numeric(MA1_TRAIN[ci,2:l+1]), type="l", col=i,
       ylim=c(-5,5))
  if (i<classes){par(new=TRUE)}
  c = c+n
}
```
# ARIMA()

```{r}
# parameters list (classes)
parameters = c(-.9, -.7, -.5, -.3, -.1, .1, .3, .5, .7, .9)

# create a empty matrix for lead time series
classes = length(parameters) #
n = 200  #number of time series per class
l = 1000 #time series legth 
ARI1_TRAIN = matrix(0, classes*n, l+1) 
ARI1_TEST = matrix(0, classes*n, l+1)

# create time series
c = 1
for (cla in 1:classes) {
  p = parameters[cla]
  
  for (i in 1:n){
    ARI1_TRAIN[c,] = arima.sim(n=l, list(order=c(1,1,0), ar=p)) #el primer valor es cero siempre.
    ARI1_TRAIN[c,1] = cla #reemplzamos el cero por la clase
    ARI1_TEST[c,] = arima.sim(n=l, list(order=c(1,1,0), ar=p))
    ARI1_TEST[c,1] = cla
    c = c+1
  }
}

ARI1_TRAIN = data.frame(ARI1_TRAIN)
colnames(ARI1_TRAIN)[1] = "clase"
ARI1_TEST = data.frame(ARI1_TEST)
colnames(ARI1_TEST)[1] = "clase"
```

```{r}
c = 0
for (i in 1:3){
  ci = c+i
  plot(as.numeric(ARI1_TRAIN[ci,2:l+1]), type="l", col=i,
       ylim=c(-5,5))
  if (i<classes){par(new=TRUE)}
  c = c+n
}
```

```{r}
write.csv(AR1_TEST, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/AR1_TEST-1000.csv", row.names=FALSE)
write.csv(AR1_TRAIN, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/AR1_TRAIN-1000.csv", row.names=FALSE)
```
```{r}
write.csv(MA1_TEST, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/MA1_TEST-1000.csv")
write.csv(MA1_TRAIN, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/MA1_TRAIN-1000.csv", row.names=FALSE)
```
```{r}
write.csv(ARI1_TEST, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/ARIMA_TEST-1000.csv", row.names=FALSE)
write.csv(ARI1_TRAIN, "C:/Users/Usuario/Google Drive (juancbellassai@mi.unc.edu.ar)/Juanc Doctorado/Base de datos/AR1-MA1-ARIMA_simulados/ARIMA_TRAIN-1000.csv", row.names=FALSE)
```
